ManuscriptPURFits

### 2024-03-01 Code/ManuscriptPURFits.Rmd
standardized variable names for ggplot labels across rmds
Renamed plot to be consistent with other plot names

MyWavelengths = c("WW", 660, 530, 450)
MCMIXColours = c("black", w_length2rgb(660), w_length2rgb(530),  w_length2rgb(450))

@@

#   mutate(PhotoperiodLabel_title = "Photoperiod (h)",

@@

# AllStrainPurFitsPlots <- plot_grid(MED4PURFITPlot, SS120PURFITPlot, MIT9313PURFITPlot, ncol = 1)
# 
# #create common x and y labels
# y.grob <- textGrob("Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")",
#                    gp = gpar(col="black", fontsize = 15), rot = 90)
# 
# #add to plot
# AllStrainPurFitsPlots <- grid.arrange(arrangeGrob(AllStrainPurFitsPlots, left = y.grob))

@@

AllStrainPurFitsPlots <- AllFitsCombined |>

@@

  mutate(PhotoperiodLabel_title = "Photoperiod (h)",

@@

AllStrainPurFitsPlots

# This labels each pane with a letter but turns of the dacet labels
# AllStrainPurFitsPlots <- tag_facet(AllStrainPurFitsPlots, open = "", close = "", tag_pool = LETTERS, size = 8)

@@

ggsave(file = file.path(PlotsOut, paste("AllStrainPurFitsPlots",".png",sep = "")), plot = AllStrainPurFitsPlots, device = NULL, scale = 1, height=30, width= 44, units = c("cm"),dpi = 300, limitsize = TRUE)

ggsave(file = file.path(PlotsOut, paste("AllStrainPurFitsPlots",".tiff",sep = "")), plot = AllStrainPurFitsPlots, device = NULL, scale = 1, height=30, width= 44, units = c("cm"),dpi = 300, limitsize = TRUE)

>>>>

MyWavelengths = c("WW", 660, 530, 450)
MCMIXColours = c("black", "#f40d30", w_length2rgb(530),  w_length2rgb(450))

@@

#   mutate(PhotoperiodLabelTitle = "Photoperiod (h)",

@@

# PhotoperiodPurFitsPlots <- plot_grid(MED4PURFITPlot, SS120PURFITPlot, MIT9313PURFITPlot, ncol = 1)
# 
# #create common x and y labels
# y.grob <- textGrob("Chlorophyll Specific Growth Rate " ~  " ("  ~ d^-1~")",
#                    gp = gpar(col="black", fontsize = 15), rot = 90)
# 
# #add to plot
# PhotoperiodPurFitsPlots <- grid.arrange(arrangeGrob(PhotoperiodPurFitsPlots, left = y.grob))

@@

PhotoperiodPurFitsPlots <- AllFitsCombined |>

@@

  mutate(PhotoperiodLabelTitle = "Photoperiod (h)",

@@

PhotoperiodPurFitsPlots

# This labels each pane with a letter but turns of the dacet labels
# PhotoperiodPurFitsPlots <- tag_facet(PhotoperiodPurFitsPlots, open = "", close = "", tag_pool = LETTERS, size = 8)

@@

ggsave(file = file.path(PlotsOut, paste("PhotoperiodPurFitsPlots",".png",sep = "")), plot = PhotoperiodPurFitsPlots, device = NULL, scale = 1, height=30, width= 44, units = c("cm"),dpi = 300, limitsize = TRUE)

ggsave(file = file.path(PlotsOut, paste("PhotoperiodPurFitsPlots",".tiff",sep = "")), plot = PhotoperiodPurFitsPlots, device = NULL, scale = 1, height=30, width= 44, units = c("cm"),dpi = 300, limitsize = TRUE)
